Discussion Draft

### 2020-03-27 doc/Discussion.rmd
small notes

#-replicate some previous results
#(Gruhn et al), Kong et al?, cattle,

@@

#sources of within mouse variance; age effects,  Hassold hunt

#models that predict more within animal variance

>>>>

@@

#models that predict more within animal variance
#none of the models expliciltly predict fr traits at the between cell level
#so any between cell variation -- patterns is due to DIFFERENCES IN THE STRENGTH OF SELECTION
